---
title: "Testing the `gluedown` package"
author: "Eric Milgram, PhD"
date: "1/12/2022"
output: html_document
---

```{r setup, include=FALSE}
library(gluedown)

knitr::opts_chunk$set(echo = TRUE, include = TRUE)
```

I'm testing the `gluedown` package, which appears to be the perfect solution
I've been been searching for to use `rmarkdown` to create *Github Flavored
Markdown* (*GFM*)

Start by reviewing the `gluedown` *package vignette* on creating *GFM*. If you
have a version of `gluedown` with the *vignettes* installed, take the following
actions to view it.

1.  Execute `browseVignettes("gluedown")` in your `R` "console window".
2.  In the row with the text, "*GitHub Flavored Markdown*", click the hyperlink
    named`HTML`.
3.  The code block below was copied from that document.

```{r}
rescale01 <- function(x) {
  rng <- range(x, na.rm = TRUE)
  (x - rng[1]) / (rng[2] - rng[1])
}

# use deparse() to turn unevaluated expressions into character strings.
source <- deparse(rescale01)
# this new object is a regular character vector
print(source)
```

```{r}
md_indent(source)
```

```{r echo=FALSE, results='asis'}
md_indent(source)
```

Here is another example taken from a later portion of the same vignette.

`CODE -> START HERE`

---
```{code}
        You can also use `gluedown` to format R [inline code results][inline]. First,
        use R to calculate a result.

        ```{r ex_inline}
        rand <- sample(state.name, 1)
        # `r md_bold(rand)`
        var <- sample(colnames(state.x77), 1)
        # `r md_code(var)`
        ```

        Then, you can easily print that result in the middle of regular text with
        markdown formatting. In this case, our randomly selected state is... 
        `r md_bold(rand)` and the `r md_code(var)` variable was randomly selected from
        the `state.x77` dataframe. Calculating results and using those
        calculations in the body of a text document increases reproducibility. 

        In a [meta-study of psychology journals][pmc], researchers found that "around
        15% of the articles contained at least one statistical conclusion that proved,
        upon recalculation, to be incorrect." These errors can be mitigated by using
        inline printing of results like we did above. With the `gluedown` package,
        programmers can **emphasize** those results without worry.

        [pmc]: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3174372/
```

---

`CODE -> END HERE`

---

`OUTPUT --> START HERE`

---

You can also use `gluedown` to format R [inline code results][inline]. First,
use R to calculate a result.

```{r ex_inline}
rand <- sample(state.name, 1)
# `r md_bold(rand)`
var <- sample(colnames(state.x77), 1)
# `r md_code(var)`
```

Then, you can easily print that result in the middle of regular text with
markdown formatting. In this case, our randomly selected state is... 
`r md_bold(rand)` and the `r md_code(var)` variable was randomly selected from
the `state.x77` dataframe. Calculating results and using those
calculations in the body of a text document increases reproducibility. 

In a [meta-study of psychology journals][pmc], researchers found that "around
15% of the articles contained at least one statistical conclusion that proved,
upon recalculation, to be incorrect." These errors can be mitigated by using
inline printing of results like we did above. With the `gluedown` package,
programmers can **emphasize** those results without worry.

[pmc]: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3174372/

---

`OUTPUT --> END HERE`
