---
title: "Testing the `gluedown` package"
author: "Eric Milgram, PhD"
date: "1/12/2022"
output: html_document
---

```{r setup, include=FALSE}
library(gluedown)

knitr::opts_chunk$set(echo = TRUE)
```

I'm testing the `gluedown` package, which appears to be the perfect solution
I've been been searching for to use `rmarkdown` to create *Github Flavored
Markdown* (*GFM*)

Start by reviewing the `gluedown` *package vignette* on creating *GFM*. If you
have a version of `gluedown` with the *vignettes* installed, take the following
actions to view it.

1.  Execute `browseVignettes("gluedown")` in your `R` "console window".
2.  In the row with the text, "*GitHub Flavored Markdown*", click the hyperlink
    named`HTML`.
3.  The code block below was copied from that document.

```{r}
rescale01 <- function(x) {
  rng <- range(x, na.rm = TRUE)
  (x - rng[1]) / (rng[2] - rng[1])
}

# use deparse() to turn unevaluated expressions into character strings.
source <- deparse(rescale01)
# this new object is a regular character vector
print(source)
```

```{r}
md_indent(source)
```

```{r echo=FALSE, results='asis'}
md_indent(source)
```


